### 2016-03-16 paper.tex
Add commented bib file back to paper.tex
Remove myself as corresponding author
Uncomment figures

{\Large \textbf\newline{Experimental Study of a Reference Model Vertical-Axis
        Cross-Flow Turbine}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03824, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

% Use the asterisk to denote corresponding authorship and provide email address
% in note below.
*pxL3@unh.edu (PB), *martin.wosnik@unh.edu (MW)

@@

\begin{figure}[h]
    % \includegraphics[width=0.65\textwidth]{figures/turbine.eps}

@@

\begin{figure}
    % \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}

@@

    % \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}

@@

    % \includegraphics[clip,trim=0.01in 0 0 0, width=\textwidth]{figures/tank_cross_section}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}

@@

\begin{figure}
    % \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}

@@

\begin{figure}
    % \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/perf_covers.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/no_blades_all.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/meancontquiv.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}

@@

\begin{figure}
    % \includegraphics[width=\textwidth]{figures/k_contours.eps}

@@

\begin{figure}
    % \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}

@@

% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%
\bibliographystyle{plos2015}
\begin{thebibliography}{10}

>>>>

{\Large \textbf\newline{Experimental Study of a Reference Model Vertical-Axis
        Cross-Flow Turbine}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03824, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

% Use the asterisk to denote corresponding authorship and provide email address
% in note below.
*martin.wosnik@unh.edu

@@

\begin{figure}[h]
    \includegraphics[width=0.65\textwidth]{figures/turbine.eps}

@@

\begin{figure}
    \includegraphics[width=0.95\textwidth]{figures/strut_covers.eps}

@@

    \includegraphics[width=0.95\textwidth]{figures/exp-setup-photo}

@@

    \includegraphics[clip,trim=0.01in 0 0 0, width=\textwidth]{figures/tank_cross_section}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/turbine_coordinate_system.eps}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures/cp_curves.eps}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures/cd_curves.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/perf_re_dep.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/perf_covers.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/no_blades_all.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-meancontquiv_10.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/meancontquiv.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/RVAT-Re-dep-k_contours_10.eps}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{figures/k_contours.eps}

@@

\begin{figure}
    \includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph.eps}

@@

% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%
\bibliographystyle{plos2015}
%\bibliography{library}
\begin{thebibliography}{10}
